Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-07 arxiv/proof_examples.tex
revise

%\subsubsection{Proof for Sample Imbalance}
We provide the proof of Proposition \ref{cor_MTL_loss}. Similar to the proof of Theorem \ref{thm_many_tasks}, our proof is divided into the following parts:
\begin{itemize}
\item First, we reduce the optimization objective to another function $g(x)$ that only depends on the sample covariance matrices.
\item Second, we show that the global minimizer of $g(x)$ is approximate $1$.
\item Finally, we use the above result and Theorem \ref{thm_main_RMT} to prove the proposition.
\end{itemize}

@@

 Now inserting $\hat B$ back into equation \eqref{eq_mtl_2task_cov}, we obtain an objective that only depends on $A:=A_1/A_2$ as follows \HZ{$A$ has been used to denote the output layers. Could you replace $A$ with another symbol (say $x$)?}

@@

		 g(A) \define & \left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)+ \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} + A X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
		 + & \left\| X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)+ \left(X^{(2)}\Sigma(A)^{-1} (X^{(2)})^\top-\id_{n_2}\right)\epsilon^{(2)} + A X^{(2)}\Sigma(A)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2, 

@@

	\HZ{the above Eq is overline}
	where we denote
	$$ \Sigma(A):= A^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$$

>>>>

%\subsubsection{Proof for Sample Imbalance}
We provide the proof of Proposition \ref{cor_MTL_loss}. Similar to the proof of Theorem \ref{thm_many_tasks}, our proof is divided into the following parts:
\begin{itemize}
\item First, we reduce the optimization objective to another function $g(x)$ that only depends on the sample covariance matrices.
\item Second, we show that the global minimizer of $g(x)$ is approximately equal to $1$.
\item Finally, we use the above result and Theorem \ref{thm_main_RMT} to prove the proposition.
\end{itemize}

@@

 Now inserting $\hat B$ back into equation \eqref{eq_mtl_2task_cov}, we obtain an objective that only depends on $x:=A_1/A_2$ as follows %\HZ{$A$ has been used to denote the output layers. Could you replace $A$ with another symbol (say $x$)?}

@@

		 g(x) \define & \left\| X^{(1)} \Sigma(x)^{-1} (X^{(2)})^\top X^{(2)} (x\beta_2-\beta_1)+ \left(x^2 X^{(1)}\Sigma(x)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} \right. \nonumber\\
		& \left. + x X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
		 + & \left\| X^{(2)} \Sigma(x)^{-1} (X^{(1)})^\top X^{(1)} (x\beta_1-x^2\beta_2)+ \left(X^{(2)}\Sigma(x)^{-1} (X^{(2)})^\top-\id_{n_2}\right)\epsilon^{(2)} \right. \nonumber\\
		 &\left. + x X^{(2)}\Sigma(x)^{-1} (X^{(1)})^\top \epsilon^{(1)} \right\|^2, 

@@

	where we denote {\cor revise}
	$$ \Sigma(x):= x^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$$
